---
title: "Preprocess"
output: html_document
---

# Call some libraries

```{r , message=FALSE}
library(mice)
library(MASS)
library(ggplot2)
library(dplyr)
library(DMwR)
library(grid)
```

# Read data

```{r}
data<-read.csv("./../data/framingham.csv",header=T)
head(data)
```

# Dealing with missing values

We first deal with the missing data in the dataset.

```{r}
# We can use the next command to explore the distribution of missing values
#md.pattern(data[!complete.cases(data),])
```


The outcome of missing data:

Missing values: heartRate:1,BMI:19,cigersPerDay:29,totChol:50,BPMeds:53,education:105,glucose:388.


## HeartRate

Use median to impute.

```{r}
summary(data[,'heartRate'])
data[is.na(data$heartRate),"heartRate"]<-median(data$heartRate,na.rm=T)
```

## cigersPerDay

Use median to impute. Note that cigerPerDay has strong relationship with currentSmoker. 

```{r}
sum(data$currentSmoker==0 & is.na(data$cigsPerDay))
sum(data$currentSmoker==0 & data$cigsPerDay!=0)
summary(data$cigsPerDay)
summary(data[data$cigsPerDay>0,]$cigsPerDay)
data[is.na(data$cigsPerDay),"cigsPerDay"]<-20
```

## BPMeds

Use Fisher's lda to impute. We know BPMeds has strong relationship with sysBP and diaBP by piror knowledge.

```{r}
data$BPMeds<-as.factor(data$BPMeds)
table(data$BPMeds,exclude=(useNA="ifany"))
data_BP<-data[!is.na(data$BPMeds),c("sysBP","diaBP","BPMeds")]
colMeans(data_BP[data_BP$BPMeds==1,1:2])
colMeans(data_BP[data_BP$BPMeds==0,1:2])
```

A boxplot of BPMeds~sysBP and diaBP.

```{r}
p1<-ggplot(data=data_BP,aes(x=as.factor(BPMeds),y=sysBP,group=BPMeds,fill=BPMeds))+geom_boxplot()+xlab("BPMeds")
p2<-ggplot(data=data_BP,aes(x=as.factor(BPMeds),y=diaBP,group=BPMeds,fill=BPMeds))+geom_boxplot()+xlab("BPMeds")
grid.newpage()
pushViewport(viewport(layout = grid.layout(nrow=1,ncol=2)))
vplayout <- function(x,y){viewport(layout.pos.row = x,layout.pos.col = y)}
print(p1,vp=vplayout(1,1))
print(p2,vp=vplayout(1,2))
```

The scatter plot of diaBP and sysBP by BPMeds.

```{r}
data$BPMeds<-as.factor(data$BPMeds)
ggplot(data=data_BP,aes(x=sysBP,y=diaBP,colour=BPMeds))+geom_point()
```

```{r}
cls<-lda(BPMeds~sysBP+diaBP,data=data_BP)
table(data_BP$BPMeds,predict(cls,data=data_BP)$class)
data[is.na(data$BPMeds),"BPMeds"]<-predict(cls,data[is.na(data$BPMeds),c("sysBP","diaBP")])$class
any(is.na(data$BPMeds))
```

## BMI, totChol, glucose

Use knn to impute and use cross validation to choose k.

```{r}
## This chunk need large amounts of time to run. We use MSE to choose k. We choose k=20 at last. The outcome of the chunk will not affect chunks behind it.

#data_knn<-data[,c("age","sysBP","diaBP","heartRate","BMI","totChol","glucose")]
#data_knn_complete<-data_knn[complete.cases(data_knn),]
#set.seed(2020)
#data_knn_complete$col<-sample(dim(data_knn_complete)[1])%%5+1
#MSE<-matrix(0,ncol=1,nrow=200)
#for(k in 1:50){
#  for(i in 1:5){
#    tmp<-data_knn_complete
#    std<-tmp[tmp$col==i,c("BMI","totChol","glucose")]
#    tmp[tmp$col==i,c("BMI","totChol","glucose")]<-NA
#    tmp[,-8]<-knnImputation(tmp[,-8],k=k,meth="weighAvg")
#    MSE[k,1]<-MSE[k,1]+sum((std-tmp[tmp$col==i,c("BMI","totChol","glucose")])^2)
#  }
#}
```


We use k=20 to do the knn imputation.

```{r}
data[,c("age","sysBP","diaBP","heartRate","BMI","totChol","glucose")]<-
  knnImputation(data[,c("age","sysBP","diaBP","heartRate","BMI","totChol","glucose")],k=20,meth="weighAvg")
data$BMI<-round(data$BMI,2)
data$totChol<-round(data$totChol,0)
data$glucose<-round(data$glucose,0)
```

## Education

Use mode to impute. The chi-square test shows education does not have difference between levels.

```{r}
table(data$education,data$TenYearCHD)/rowSums(table(data$education,data$TenYearCHD))
chisq.test(table(data$education,data$TenYearCHD))
data[is.na(data$education),"education"]<-1
```

# Test and write data

```{r}
any(is.na(data))
write.csv(data,"./../data/preprocess.csv",row.names=F)
```

