---
title: "EDA and Smote"
output: html_document
---

# Call some libraries

```{r , message=FALSE}
library(ggplot2)
library(MASS)
library(pROC)
library(caret)
library(DMwR)
```

# Read data

```{r}
data<-read.csv("./../data/preprocess.csv",header=T)
data<-data[,-4]
data$TenYearCHD<-as.factor(data$TenYearCHD)
any(is.na(data))
head(data)
```

# Data Visualization

## Response Variable

The distribution of the response variable is very unbalanced (85 v.s. 15).

```{r}
prop.table(table(data$TenYearCHD))
```

## sysBP

```{r}
ggplot(data=data,aes(x=as.factor(TenYearCHD),y=sysBP,fill=TenYearCHD))+geom_boxplot(varwidth=T)+xlab("CHD")

```

## cigsPerDay

```{r}
ggplot(data=data,aes(x=as.factor(TenYearCHD),y=cigsPerDay,fill=TenYearCHD))+geom_boxplot(varwidth=T)+xlab("CHD")

```

## Age

```{r}
ggplot(data=data,aes(x=as.factor(TenYearCHD),y=age,fill=TenYearCHD))+geom_boxplot(varwidth=T)+xlab("CHD")

```


# Train-test Split

We split the dataset into train data and test data with porprotion (80&20).

```{r}
set.seed(2020)
ind<-sample(1:nrow(data),size=0.8*nrow(data))
test<-data[-ind,]
train<-data[ind,]
table(train$TenYearCHD)
table(test$TenYearCHD)
```

# Logistic Regression without Oversampling

We first train a logistic regression on the unbalanced data. We will find some problems on the naive model

```{r}
for(i in c(1,3,5,6,7,8,15)){
  train[,i]<-as.factor(train[,i])
  test[,i]<-as.factor(test[,i])
}
```

## Model

```{r results='hide'}
fit_lr<-glm(TenYearCHD~.,data=train,family=binomial(link="logit"))
fit_lr<-stepAIC(fit_lr)
```

```{r}
summary(fit_lr)
```

## Prediction on Train Set

```{r}
pred_fit1<-predict(fit_lr,data=train[,-15],type="response",quiet=T)
roc_train_fit1<-roc(train$TenYearCHD,pred_fit1)
plot(roc_train_fit1,print.auc=T,auc.polygon=TRUE,max.auc.polygon=TRUE,grid=c(0.1,0.2),
     auc.polygon.col="skyblue", print.thres=TRUE)
opt<-coords(roc=roc_train_fit1,x="best",ret="threshold",best.method="closest.topleft")
pred_fit1<-ifelse(pred_fit1<opt,0,1)
confusionMatrix(data=as.factor(pred_fit1),reference=as.factor(train$TenYearCHD))

```


## Prediction on Test Set

```{r}
pred_fit1_test<-predict(fit_lr,newdata=test[,-15],type="response",quiet=T)
pred_fit1_test<-ifelse(pred_fit1_test<opt,0,1)
roc_test_fit1<-roc(test$TenYearCHD,pred_fit1_test)
plot(roc_test_fit1,print.auc=T,auc.polygon=TRUE,max.auc.polygon=TRUE,grid=c(0.1,0.2),
     auc.polygon.col="skyblue")
confusionMatrix(data=as.factor(pred_fit1_test),reference=as.factor(test$TenYearCHD))

```

# SMOTE

We will use SMOTE to oversample the data. After oversampling, the positive samples and the negative samples will have the same porprotion.

## Hyperparameters

Find the best hyperparameters in SMOTE. We use AUC on the test set to choose hyperparameters.

```{r}
## This chunk need many time to run. We will jump this chunk in Rmd.

#k<-1:8
#perc.over<-seq(from=100,to=300,by=25)
#iter<-matrix(NA,nrow=length(k),ncol=length(perc.over))

#for(j in 1:length(perc.over)){
#  for (i in 1:length(k)) {
#    set.seed(2020)
#    train_smote<-SMOTE(TenYearCHD~.,train,perc.over=perc.over[j],k=k[i],perc.under=100*(100+perc.over[j])/perc.over[j])
#    fit_smote<-glm(formula=TenYearCHD~.,data=train_smote,family = binomial(link="logit"))
#    pred_train_smote<-predict(object=fit_smote,newdata=train_smote,type="response")
#    auc_train_smote<-auc(train_smote$TenYearCHD,pred_train_smote,quiet=T)
#    iter[i,j]<-as.numeric(auc_train_smote)
#  }
#}
#which(iter==iter[which.max(iter)],arr.ind=T)
```

## Oversampling


```{r}
set.seed(2020)
train_smote<-SMOTE(TenYearCHD~.,train,perc.over=300,k=1,perc.under=100*(100+300)/300)
```

# Logistic Regression on the Oversampled Data

```{r results='hide'}
fit_smote<-glm(formula=TenYearCHD~.,data=train_smote,family = binomial(link="logit"))
fit_smote<-stepAIC(fit_smote)
```

```{r}
summary(fit_smote)
```

## Prediction on Train Set

```{r}
pred_train_smote<-predict(object=fit_smote,newdata=train_smote,type="response")
roc_train_smote<-roc(train_smote$TenYearCHD,pred_train_smote)
plot(roc_train_smote,print.auc=T,auc.polygon=TRUE,max.auc.polygon=TRUE,grid=c(0.1,0.2),
     auc.polygon.col="skyblue", print.thres=TRUE)
opt_smote<-coords(roc=roc_train_smote,x="best",ret="threshold",best.method="closest.topleft")
pred_train_smote<-ifelse(pred_train_smote<opt_smote,0,1)
confusionMatrix(data=as.factor(pred_train_smote),reference=as.factor(train_smote$TenYearCHD))
```

## Prediction on Test Set

```{r}
pred_test_smote<-predict(object=fit_smote,newdata=test,type="response")
roc_test_smote<-roc(test$TenYearCHD,pred_test_smote)
plot(roc_test_smote,print.auc=T,auc.polygon=TRUE,max.auc.polygon=TRUE,grid=c(0.1,0.2),
     auc.polygon.col="skyblue", print.thres=TRUE)
pred_test_smote<-ifelse(pred_test_smote<opt_smote,0,1)
confusionMatrix(data=as.factor(pred_test_smote),reference=as.factor(test$TenYearCHD))
```

# Write data

```{r}
write.csv(train_smote,"./../data/train with smote.csv",row.names=F)
write.csv(test,"./../data/test.csv",row.names=F)
```


